Reopt

### 2023-05-12 src/00_demographic_data_wrangling.Rmd
uploading instructional documentation for dryad

```{r population growth data wrangling}
# read in the data MSA population data from Census
msa_pop_2021_data <- read_csv(here("data","raw", "msa_2021_pop_data.csv")) %>% 
  clean_names() %>% # data wrangling to make column headers in lower_snake_case
  filter(lsad == "Metropolitan Statistical Area") %>% # select MSA cities
  select("cbsa", "name", "popestimate2020", "popestimate2021", "residual2020", "residual2021") %>% # select data 
  separate(col = "name",
           into = c("MSA", "state"), # split city and state data
           sep = ", ") %>% 
  mutate(pop_percent_change = (popestimate2021-popestimate2020)/popestimate2020 * 100)  # calculate population % change

# create object with viable MSAs 
potential_MSAs <- msa_pop_2021_data %>% 
  filter(pop_percent_change > 0.5 ) %>% # select areas with population growth greater than .5%
  filter(popestimate2021 >= 500000) %>% 
  mutate(pop_percent_change20_21 = round(pop_percent_change, digits = 3)) %>% 
  filter (!state %in% c("CA", "HI", "AK")) %>% # remove areas within these states
  filter(!cbsa %in% c("10580", "10900", "12420", "12940", "14260", "15980", "18580", "19100", "19660", "19740", "23540", "25420", "26420", "27260", "29820", "34940", "36260", "36740", "38060", "39100", "39300", "39340", "41620", "45220", "45300", "46060", "46140", "39900")) %>%  # remove MSAs as instructed by client 
  select(cbsa, MSA, state, pop_percent_change20_21, popestimate2021)

@@

```{r population change visual, fig.height = 7, fig.align='center', eval = FALSE}
# create plot of MSAs sorted grom highest population growth to lowest
ggplot(data = positive_MSA_pop_change, aes(x = pop_percent_change20_21, y = reorder(MSA, pop_percent_change20_21))) + 
  geom_point(size = 3, color = "darkgreen") + 
  theme_minimal(base_size = 12.5)

@@

```{r household income data wrangling}
MSA_income_data <- read_csv(here("data","raw", "2021_income_data.csv")) %>% 
  row_to_names(1) %>% 
  clean_names() %>% 
  mutate(median_income = as.numeric(estimate_households_median_income_dollars),
  income_moe_USD = as.numeric(margin_of_error_households_median_income_dollars)) %>% 
  separate(col = "geography",
           into = c("id", 'cbsa'),
           sep = 9) %>% 
  mutate(cbsa = as.numeric(cbsa)) %>% # change column class from chr to dbl
  inner_join(potential_MSAs)

# join household median income to existing msa dataframe
potential_MSAs <- potential_MSAs %>% add_column(med_income = MSA_income_data$median_income)

@@

```{r, employment data wrangling}
unemployment_data <- read_csv(here("data", "raw", "civil_labor_force_BLS.csv")) %>% #rename col headers
  clean_names() %>% 
  rename(cbsa = x3,
         area = x4,
         year = x5,
         month = x6,
         civilian_labor_force = x7,
         employment = x8,
         unemployment = x9,
         unemployment_rate = x10)%>% 
  mutate(employment_rate = (employment/civilian_labor_force)*100) # calculate

# data wrangling, only selecting data for potential MSAs
MSA_employment <- unemployment_data %>% 
  filter(year >= 2018) %>% 
  mutate(cbsa = ifelse(cbsa == '76750', "38860", cbsa)) %>% # change south portland, ME to corresponding cbsa
  mutate(cbsa = as.numeric(cbsa)) %>% 
  right_join(potential_MSAs) %>% 
  group_by(MSA, year) %>% 
  summarize(avg_employment_rate = mean(employment_rate)) %>% 
  mutate(avg_emp_rate = (avg_employment_rate-lag(avg_employment_rate))/lag(avg_employment_rate)*100, 
          avg_emp_rate = round(avg_emp_rate, digits = 4)) %>% 
  drop_na() %>% 
  mutate(emp_pos = case_when( 
    avg_emp_rate > 0 ~ "TRUE",
    avg_emp_rate < 1 ~ "FALSE"))

MSA_employ_rate <- MSA_employment %>% 
  filter(year == "2021")

potential_MSAs$employ_change <- MSA_employ_rate$avg_emp_rate

@@

```{r median rent}
# data wrangling 2021 median rent
MSA_median_rent2021_data <- read_csv(here("data", "raw", "2021MSA_medianrent.csv")) %>% 
  separate(col = cbsasub21,
           into = c("metro", "cbsa"),
           sep = 5) %>% 
  separate(col = cbsa,
           into = c("unknown", "cbsa"),
           sep = -5) %>% 
  mutate(cbsa = ifelse(cbsa == 'M6400', "38860", cbsa),
        cbsa = as.numeric(cbsa) ,
        median_rent2021 = as.numeric(rent50_1)) %>% # select median rent for 1 bedroom apartments
  select(cbsa, median_rent2021) %>% 
  right_join(potential_MSAs)

# 2022 median rent
MSA_median_rent2022_data <- read_csv(here("data", "raw", "2022MSA_median_rent.csv")) %>% 
  separate(col = cbsasub22,
           into = c("metro", "cbsa"),
           sep = 5) %>% 
  separate(col = cbsa,
           into = c("unknown", "cbsa"),
           sep = -5) %>% 
  mutate(cbsa = ifelse(unknown == "38860M" & areaname22 == "Portland, ME HUD Metro FMR Area", "38860", cbsa),
         cbsa = as.numeric(cbsa),
         median_rent2022 = as.numeric(rent_50_1)) %>% 
  select(cbsa, median_rent2022) %>% 
  right_join(potential_MSAs)

potential_MSAs <- potential_MSAs %>% 
  add_column(med_rent2021 = MSA_median_rent2021_data$median_rent2021, # add rent data
             med_rent_2022 = MSA_median_rent2022_data$median_rent2022)

@@

```{r house price data}
metro_house_cost_data <- read_csv(here("data","raw", "metro_home_costs", "metro-home-prices-2022-11-10.csv")) %>% 
  row_to_names(3) %>% # make sure column headers are correct
  clean_names() %>% 
  separate(col = "metropolitan_area",
           into = c("cbsa", 'metro_area'),
           sep = 5) %>% 
  mutate(cbsa = as.numeric(cbsa),
        x2021 = as.numeric(x2021), 
        house_price_2021 = x2021 * 1000) %>% # data is proivded as thousands, so multiply to get correct ratio
  right_join(potential_MSAs) %>% 
  mutate(house_price_2021 = ifelse(cbsa == "12260", "284900", house_price_2021), 
        house_price_2021 = ifelse(cbsa == "32580", "259000", house_price_2021))

potential_MSAs$house_price_2021 <- metro_house_cost_data$house_price_2021

@@

```{r data table}
# clean up names
potential_MSAs <- potential_MSAs %>% 
  rename(pop_growth = pop_percent_change20_21)

@@

write.xlsx(potential_MSAs, here("data/intermediate/demographic.xlsx"), sheetName = "Sheet1")

#gs4_create("real_estate_inputs")
#output data into google sheet
#sheet_write(potential_MSAs, ss = "https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit#gid=0", sheet = "MSA_demographics")
```

>>>>

```{r population growth data wrangling}
# read in the data MSA population data from Census
msa_pop_2021_data <- read_csv(here("data/raw/population_est2021.csv")) %>% 
  clean_names() %>% # data wrangling to make column headers in lower_snake_case
  filter(lsad == "Metropolitan Statistical Area") %>% # select MSA cities
  select("cbsa", "name", "popestimate2020", "popestimate2021", "residual2020", "residual2021") %>% # select data 
  separate(col = "name",
           into = c("MSA", "state"), # split city and state data
           sep = ", ") %>% 
  mutate(pop_percent_change = (popestimate2021-popestimate2020)/popestimate2020 * 100)  # calculate population % change

# create object with viable MSAs for client 
potential_MSAs <- msa_pop_2021_data %>% 
  filter(pop_percent_change > 0.5 ) %>% # select areas with population growth greater than .5%
  filter(popestimate2021 >= 500000) %>% 
  mutate(pop_percent_change20_21 = round(pop_percent_change, digits = 3)) %>% 
  filter (!state %in% c("CA", "HI", "AK")) %>% # remove areas within these states
  filter(!cbsa %in% c("10580", "10900", "12420", "12940", "14260", "15980", "18580", "19100", "19660", "19740", "23540", "25420", "26420", "27260", "29820", "34940", "36260", "36740", "38060", "39100", "39300", "39340", "41620", "45220", "45300", "46060", "46140", "39900")) %>%  # remove MSAs as instructed by client 
  select(cbsa, MSA, state, pop_percent_change20_21, popestimate2021)

unfiltered_msas <- msa_pop_2021_data %>% 
  filter(pop_percent_change>0.5) %>% 
  select(1:3, pop_percent_change)
```

@@

@@

```{r household income data wrangling}
MSA_income_data <- read_csv(here("data/raw/income_data2021.csv")) %>% 
  row_to_names(1) %>% 
  clean_names() %>% 
  mutate(median_income = as.numeric(estimate_households_median_income_dollars),
  income_moe_USD = as.numeric(margin_of_error_households_median_income_dollars)) %>% 
  separate(col = "geography",
           into = c("id", 'cbsa'),
           sep = 9) %>% 
  mutate(cbsa = as.numeric(cbsa)) %>% # change column class from chr to dbl
  select(cbsa, median_income)

# join household median income to existing msa dataframe
potential_MSAs <- potential_MSAs %>% 
  inner_join(MSA_income_data)

unfiltered_msas <- unfiltered_msas %>% inner_join(MSA_income_data)
```

@@

```{r, employment data wrangling}
unemployment_data <- read_csv(here("data/raw/unemployment_data.csv")) %>% #rename col headers
  clean_names() %>% 
  rename(cbsa = x3,
         area = x4,
         year = x5,
         month = x6,
         civilian_labor_force = x7,
         employment = x8,
         unemployment = x9,
         unemployment_rate = x10) %>% 
  drop_na() %>% 
  mutate(employment_rate = (employment/civilian_labor_force)*100) %>%  # calculate
  select(cbsa, area, year, month, employment_rate)

# data wrangling, only selecting data for potential MSAs
MSA_employment <- unemployment_data %>% 
  filter(year >= 2018) %>% 
  mutate(cbsa = ifelse(cbsa == '76750', "38860", cbsa)) %>% # change south portland, ME to corresponding cbsa
  mutate(cbsa = as.numeric(cbsa)) %>% 
  group_by(area, cbsa, year) %>% 
 #  right_join(potential_MSAs) %>% 
  summarize(avg_employment_rate = mean(employment_rate)) %>% 
  mutate(avg_emp_rate = (avg_employment_rate-lag(avg_employment_rate))/lag(avg_employment_rate)*100, 
          avg_emp_change = round(avg_emp_rate, digits = 4)) %>% 
  filter(year=="2021") %>% 
  select(cbsa, area, avg_emp_change)

client_MSAs <-potential_MSAs %>% 
  left_join(MSA_employment)

unfiltered_msas <- unfiltered_msas %>% 
  left_join(MSA_employment)

@@

```{r median rent}
# data wrangling 2021 median rent
median_rent2021_data <- read_csv(here("data/raw/median_rent2021.csv")) %>% 
  separate(col = cbsasub21,
           into = c("metro", "cbsa"),
           sep = 5) %>% 
  separate(col = cbsa,
           into = c("unknown", "cbsa"),
           sep = -5) %>% 
  mutate(cbsa = ifelse(cbsa == 'M6400', "38860", cbsa),
        cbsa = as.numeric(cbsa) ,
        median_rent2021 = as.numeric(rent50_1)) %>% # select median rent for 1 bedroom apartments
  select(cbsa, median_rent2021)

# 2022 median rent
median_rent2022_data <- read_csv(here("data", "raw", "median_rent2022.csv")) %>% 
  separate(col = cbsasub22,
           into = c("metro", "cbsa"),
           sep = 5) %>% 
  separate(col = cbsa,
           into = c("unknown", "cbsa"),
           sep = -5) %>% 
  mutate(cbsa = ifelse(unknown == "38860M" & areaname22 == "Portland, ME HUD Metro FMR Area", "38860", cbsa),
         cbsa = as.numeric(cbsa),
         median_rent2022 = as.numeric(rent_50_1)) %>% 
  select(cbsa, areaname22, median_rent2022) %>% 
  left_join(median_rent2021_data)

client_msas <-client_MSAs %>% 
  left_join(median_rent2022_data)

unfiltered_msas <- unfiltered_msas %>% 
  left_join(median_rent2022_data)

@@

```{r house price data}
metro_house_cost_data <- read_csv(here("data/raw/metro-home-prices-2022.csv")) %>% 
  row_to_names(3) %>% # make sure column headers are correct
  clean_names() %>% 
  separate(col = "metropolitan_area",
           into = c("cbsa", 'metro_area'),
           sep = 5) %>% 
  mutate(cbsa = as.numeric(cbsa),
        x2021 = as.numeric(x2021), 
        house_price_2021 = x2021 * 1000) %>% # data is proivded as thousands, so multiply to get correct ratio
  mutate(house_price_2021 = ifelse(cbsa == "12260", "284900", house_price_2021), 
        house_price_2021 = ifelse(cbsa == "32580", "259000", house_price_2021)) %>% 
  select(cbsa, house_price_2021)

potential_MSAs <- client_msas %>% 
  left_join(metro_house_cost_data)

unfiltered_msas <- unfiltered_msas %>% 
  left_join(metro_house_cost_data)

@@

```{r data table}
# clean up names
potential_MSAs <- potential_MSAs %>% 
  select(-area, -areaname22)

unfiltered_msas <- unfiltered_msas %>% select(-area, -areaname22)

@@

#write_csv(potential_MSAs, here("data/intermediate/demographic_data.csv"))

### 2023-05-12 src/reopt_api.Rmd
uploading instructional documentation for dryad

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(RJSONIO)
library(jsonlite)
```

### Obtain MSA zip code information
```{r}
token <- "eyJ0eXAiOiJKV1QiLCJhbGciOiJSUzI1NiIsImp0aSI6ImNmMmU0Yzg1ZWZlMDNiYTkxNTA4YzdlNWJiYjE1NjVkNzIyNjg4MzgwYTE4OWNjNmJkOWRjNjFiZWUyZjIwYzg0ZmJjNmZkOTc0MDg4YzRmIn0.eyJhdWQiOiI2IiwianRpIjoiY2YyZTRjODVlZmUwM2JhOTE1MDhjN2U1YmJiMTU2NWQ3MjI2ODgzODBhMTg5Y2M2YmQ5ZGM2MWJlZTJmMjBjODRmYmM2ZmQ5NzQwODhjNGYiLCJpYXQiOjE2ODI0ODQyOTYsIm5iZiI6MTY4MjQ4NDI5NiwiZXhwIjoxOTk4MTAzNDk2LCJzdWIiOiI0ODUyMyIsInNjb3BlcyI6W119.G7NL2Khpo602p_fzk6EiAZ0-KdXsVW-IO9mUqwHem0YFLaTQZezotmLqXmbcTi7BxRzc8UHNYBw415CCzKo81w"

@@

# zip-cbsa : type3
zip_url <- "https://www.huduser.gov/hudapi/public/usps?type=3&query=All"

@@

# make data frame
cbsa_city_data <- data.frame("geoid"= response_cbsa$data$results$geoid,
                             "cbsa"= response_cbsa$data$results$cbsa,
                            "city"= response_cbsa$data$results$city)

zip_response <- GET(url = zip_url ,add_headers("Authorization" = paste("Bearer", token)))
# Extract the response content as JSON and convert it to a list
response_zip_content <- content(zip_response, as="text")
response_list <- fromJSON(response_zip_content)

zip_data <- data.frame("geoid"= response_list$data$results$geoid,
                            "zipcode"= response_list$data$results$zip,
                             "state"= response_list$data$results$state)
# combine data sets
zip_cbsa_data <- cbsa_city_data %>% 
  right_join(zip_data)

@@

```{r polulation estimates}
api_key <- "ebab921b3002df9b71881ad6c426f34281ce0e11"
# Add key to .Renviron
Sys.setenv(CENSUS_KEY="ebab921b3002df9b71881ad6c426f34281ce0e11")
# Reload .Renviron
readRenviron("~/.Renviron")
# Check to see that the expected key is output in your R console
Sys.getenv("CENSUS_KEY")

@@

msa_zip_pop_est_data <- pop_list %>% 
  left_join(cbsa_city_data) %>% 
  inner_join(zip_data)

# reopt inputs
```{r}
# create list of default inputs for each city
inputs <- list(
  offtaker_tax_pct = 0, # host effective tax rate
  co2_cost_us_dollars_per_tonne = 185,
  module_type = 1,
  dc_ac_ratio = 1.35,
  losses = 0.05,
  federal_itc_pct = 0.3,
  location = "roof", # restrict projects to roof
  can_net_meter = TRUE

)
```

# Set the payload for the job submission request for reopt
```{r}
# Set the payload for the job submission request
payload <- list(
  "Scenario" = list(
    "Site" = list(
      "longitude" = -118.1164613,
      "latitude" = 34.5794343,
      "roof_squarefeet" = 5000.0,
      "PV" = list(
        "installed_cost_us_dollars_per_kw" = 2000.0,
        "federal_rebate_us_dollars_per_kw" = 350.0,
        # changes from default
        "module_type" = 1,
        "dc_ac_ratio" = 1.35, # changed default
        "losses" = 0.05,   # changed default
        "federal_itc_pct" = 0.3,  # changed default
        "location" = "roof", # restrict projects to roof
        "can_net_meter" = TRUE
      ),
      "LoadProfile" = list(
        "doe_reference_name" = "MidriseApartment",
        "annual_kwh" = 10000000.0,
        "city" = "LosAngeles"
      ),
      "ElectricTariff" = list(
        "urdb_label" = "5ed6c1a15457a3367add15ae",
        "add_tou_energy_rates_to_urdb_rate" = TRUE
      ),
      "Financial" = list(
        "escalation_pct" = 0.026,
        "offtaker_discount_pct" = 0.081,
        "owner_discount_pct" = 0.081,
        "analysis_years" = 20,
        "offtaker_tax_pct" = 0.4,
        "owner_tax_pct" = 0.4,
        "om_cost_escalation_pct" = 0.025
      )
    )
  )
)

@@

startdates <- EIutility_df$start_date
start_dates_rev <- lapply(startdates, function(x) as.Date(x/86400, origin="1970-01-01"))

@@

```{r}
## function to select the most recent utiilty rate information for a given area code
get_zip_utility <- function(zipcode){
  openEI_start_url <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address="
openEI_api_end <- "&api_key=rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"
zipcode=zipcode

  openEI_url <- paste0(openEI_start_url, zipcode, openEI_api_end)
  response <- GET(openEI_url)
  # extract content and parse as JSON
  content <- content(EIresponse, "text")
  json <- fromJSON(content)

  utility_df <- data.frame(
  # repeat zipcode in each row for each utility observation
  "zipcode" = rep(zipcode, each=nrow(json$items$label)),
  "start_date" = utility_data$items$startdate,
  "label" = json$items$label,
    "utility" = json$items$utility,
    "rate_name" = json$items$name)

  # Find index of row with most recent start date value
  max_index <- which.max(utility_df$start_date)

# Extract row with greatest seconds value
  max_row <- utility_df[max_index, ]

}

@@

@@

```{r}
# Define a vector of zip codes
zipcodes <- c("90210", "10001", "60601", "90245", "90001", "90250", "90260", "90278", "90501", "90502")

# Initialize an empty list to store the results
utility_list <- list()

# Loop through each zip code and call the get_zip_utility function
for (zipcode in zipcodes) {
  utility_data <- get_zip_utility(zipcode)
  utility_list[[zipcode]] <- utility_data
}

# Combine the results into a single data frame
utility_df <- do.call(rbind, utility_list)

@@

```{r STUFF TO WORK ON}

net_metering_limit_kw # by state
```

@@

job_url <- paste0(url, "?api_key=", api_key)
```

@@

# pull out IMPORTANT data
output_df <- data.frame(
  IRR = response_json$outputs$Scenario$Site$Financial$irr_pct,
  Health_Emissions_Cost = response_json$outputs$Scenario$Site$lifecycle_emissions_cost_Health_bau,
  Annual_Generation_Renewables = response_json$outputs$Scenario$Site$annual_renewable_electricity_pct)

@@

```{r}
#PV & wind space available:  ❌ Land only ✅ Roofspace only ❌ Land & roofspace

#PV System Characteristics
ModuleType= Premium
DCACratio = 1.35
System_losses = 5
FederalIncentive= 30

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(RJSONIO)
library(jsonlite)
library(openxlsx)
library(writexl)
library(here)
library(tidyverse)
library(janitor)
```

### Obtain MSA city information
Only used once to generate table and output results into data/intermediate folder to decrease runtime for the APi

```{r, eval= FALSE}
token <- "eyJ0eXAiOiJKV1QiLCJhbGciOiJSUzI1NiIsImp0aSI6ImNmMmU0Yzg1ZWZlMDNiYTkxNTA4YzdlNWJiYjE1NjVkNzIyNjg4MzgwYTE4OWNjNmJkOWRjNjFiZWUyZjIwYzg0ZmJjNmZkOTc0MDg4YzRmIn0.eyJhdWQiOiI2IiwianRpIjoiY2YyZTRjODVlZmUwM2JhOTE1MDhjN2U1YmJiMTU2NWQ3MjI2ODgzODBhMTg5Y2M2YmQ5ZGM2MWJlZTJmMjBjODRmYmM2ZmQ5NzQwODhjNGYiLCJpYXQiOjE2ODI0ODQyOTYsIm5iZiI6MTY4MjQ4NDI5NiwiZXhwIjoxOTk4MTAzNDk2LCJzdWIiOiI0ODUyMyIsInNjb3BlcyI6W119.G7NL2Khpo602p_fzk6EiAZ0-KdXsVW-IO9mUqwHem0YFLaTQZezotmLqXmbcTi7BxRzc8UHNYBw415CCzKo81w"

@@

# zip-cbsa : type3
#zip_url <- "https://www.huduser.gov/hudapi/public/usps?type=3&query=All"

@@

# make data frame
cbsa_city_data <- data.frame("cbsa"= response_cbsa$data$results$cbsa,
                            "city"= response_cbsa$data$results$city,
                            "state"= response_cbsa$data$results$state)  
# output into excel
#write.xlsx(cbsa_city_data, here("data/intermediate/cbsa_city_data.xlsx"), sheetName = "Sheet1")
```

# read in US city with longitude and latitude data from https://simplemaps.com/data/us-cities
```{r}
uscities <- read_csv(here("data/raw/uscities.csv")) %>% 
  mutate(city = tolower(city)) %>% 
  select(state_id, city, lat, lng, population, density, zips) %>% 
  group_by(state_id, city)

city_cbsa_api_data <- read.xlsx(here("data/intermediate/cbsa_city_data.xlsx")) %>% 
   mutate(city = tolower(city)) %>% 
  group_by(state, city)

@@

# create cbsa and city data frame that was extracted using hud API
```{r}
cbsa_city_lat_long <- city_cbsa_api_data %>% 
    filter(cbsa != "99999") %>% 
  inner_join(uscities, by = join_by(state == state_id, city == city)) %>%    # removes cities without a cbsa
  distinct()

one_city_msa_data <- cbsa_city_lat_long %>% 
  group_by(cbsa) %>% 
  summarize(max_pop = max(population)) %>% 
  left_join(cbsa_city_lat_long, by=join_by(cbsa== cbsa, max_pop==population), keep=FALSE) %>% 
  # select one zipcode to run in open ei api to get utility data
  separate(col = zips,
           sep = " ",
           into = "zips",
           extra = "drop")

# get population estimates for each Metro area in 2021  using census api
```{r polulation estimates}
api_key <- "ebab921b3002df9b71881ad6c426f34281ce0e11"
# Add key to .Renviron
Sys.setenv(CENSUS_KEY="ebab921b3002df9b71881ad6c426f34281ce0e11")
# Reload .Renviron
readRenviron("~/.Renviron")
# Check to see that the expected key is output in your R console
Sys.getenv("CENSUS_KEY")

@@

MSA_w_lat_lng <- pop_list %>% 
  inner_join(cbsa_city_lat_long, by = join_by(cbsa==cbsa))

@@

@@

```{r}
# Define a vector of zip codes
zipcodes <- msa_zip_pop_est_data
# break up zipcodes to run in openEI  
zipcodes1 <- zipcodes[1:200,]

c(zipcodes1, zipcodes2, zipcodes3, zipcodes4, zipcodes5, zipcodes6)

OpenEI_zip_result <- lapply(zipcodes1$zipcode, get_zip_utility)

@@

openei_url <- paste0("https://api.openei.org/geocoding?version=latest&format=json&postalcode=", zipcode, "&countrycode=US", "&api_key=U6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA")
response <- GET(openei_url)

# Extract the content and parse as JSON
content <- content(response, "text")
json <- fromJSON(content)

@@

# Set the payload for the job submission request for reopt
```{r}

zip_utility_info <- get_zip_utility(test$zips)
zip_EI_label <- zip_utility_info$label

test <- one_city_msa_data %>% filter(city == "des moines")

payload <- list(
  "Scenario" = list(
    "Site" = list(
      "address"= test$zips,
      "longitude"= test$lng,
      "latitude" = test$lat,

      "PV" = list(# changes from default
    "module_type" = 1, # premium
    "dc_ac_ratio" = 1.35, # changed default
    "losses" = 0.05,   # changed default
    "federal_itc_pct" = 0.3,  # changed default
     "location" = "roof", # restrict projects to roof
     "can_net_meter" = TRUE
      ),
      "LoadProfile" = list(
        "doe_reference_name" = "MidriseApartment",
        "city" = test$zips
      ),
      "ElectricTariff" = list(
        "urdb_label" = zip_utility_info$label,
        "net_metering_limit_kw" = 1000
      ),
      "Financial" = list(
        "offtaker_tax_pct" = 0, # host effective tax rate
        "owner_tax_pct" = 0.0,
        "co2_cost_us_dollars_per_tonne" = 185
      ))
  )
)

@@

```{r STUFF TO WORK ON}
net_metering_limit_kw # by state

@@

job_url <- paste0(url, api_key)
```

@@

# pull out IMPORTANT data
output_df <- data.frame(
  #IRR = response_json$outputs$Scenario$Site$Financial$irr_pct,
  Health_Emissions_Cost = response_json$outputs$Scenario$Site$lifecycle_emissions_cost_Health_bau,
  Annual_Generation_Renewables = response_json$outputs$Scenario$Site$annual_renewable_electricity_pct)

host/stable/annual_kwh
doe_response <- GET(url = results_url, query = list(api_key = api_key), timeout(30))
```

@@
